Appendix

### 2019-11-12 manuscript/appendix.Rmd
better appendix subheadings
add simple scatter, replace waffle chart with bar chart

@@

Over 50 percent of our study lakes were eutrophic to hypereutrophic.

```{r data_prep, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
lg <- lagosne_load("1.087.1")
focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
                                             c("56", "57", "36", "37", "38")), 
                         stringsAsFactors = FALSE)

dt <- readRDS("../data/dt.rds") %>%
  dplyr::filter(!is.na(chla)) %>%
  mutate(trophic_state = cut(chla, 
                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
                             labels = c("oligotrophic", "mesotrophic", 
                                        "eutrophic", "hypereutrophic"))) %>%
  dplyr::select(chla, trophic_state) %>%
  group_by(trophic_state) %>%
  count() %>%
  ungroup() %>% # rowwise() %>%
  mutate(frac = (n / sum(n)) * 100)

@@

```{r trophic_state, fig.cap="Lake trophic state", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
# waffle
library(waffle)

total_cells <- 41.5
dt_waffle <- dt %>% 
  dplyr::rename(trophic_state = `Trophic State`) %>%
  tidyr::gather(key = "key", value = "value", -trophic_state) %>%
  dplyr::filter(key == "This Study") %>%
  mutate(value = floor((value / 100) * total_cells)) %>%
  arrange(trophic_state)
# sum(dt_waffle$value)
# add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%

ggplot(dt_waffle,
       aes(fill = trophic_state, values = value)) +
  geom_waffle(color = "white", size = 3, n_rows = 4, flip = FALSE) +
  # facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 1))

# highlighted regions
test <- readRDS("../data/dt.rds") %>%
  mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>%
  dplyr::filter(!is.na(chla)) %>%
  mutate(trophic_state = cut(chla, 
                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
                             labels = c("oligotrophic", "mesotrophic", 
                                        "eutrophic", "hypereutrophic"))) %>%
  dplyr::select(lagoslakeid, is_focal, chla, hu4_zoneid, trophic_state) %>%
  group_by(is_focal, trophic_state) %>%
  count() %>%
  tidyr::spread(trophic_state, n)
```

@@

## Fixed effects dotplots of non lulc models and nutrient only models

```{r re-comparison_40-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN for lakes with greater than 40% watershed agricultural land-use. Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines). Also shown is a comparison to a zero effect (dashed line).", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-comparison_40-1.pdf")
```

@@

>>>>

## Percent agriculture versus lake TP and TN

```{r ag-scatter, fig.cap="Lake nutrient concentrations versus percent watershed agriculture.", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
dt <- readRDS("../data/dt.rds")

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  ylab("TN (ug/L)") +
  xlab("Percent Agriculture"), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) +
  ylab("TP (ug/L)") +
  xlab("Percent Agriculture")
)

```

@@

Over 35 percent of our study lakes were eutrophic to hypereutrophic.

```{r data_prep, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
lg         <- lagosne_load("1.087.1")
dt         <- readRDS("../data/dt.rds")
focal_hu4s <- data.frame(hu4_zoneid = unique(dt$hu4_zoneid), 
                         stringsAsFactors = FALSE)

dt <- dt %>%
  dplyr::filter(!is.na(chla)) %>%
  mutate(trophic_state = cut(chla, 
                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
                             labels = c("oligotrophic", "mesotrophic", 
                                        "eutrophic", "hypereutrophic"))) %>%
  dplyr::select(chla, trophic_state) %>%
  group_by(trophic_state) %>%
  count() %>%
  ungroup() %>% # rowwise() %>%
  mutate(frac = (n / sum(n)) * 100)

@@

```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes in the study extent.", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}

dt_bar <- tidyr::pivot_longer(dt, -`Trophic State`) %>%
  group_by(name) %>%
  mutate(ymax = cumsum(value),           
         ymin = c(0, head(ymax, n = -1)))

ggplot(data = dt_bar) +
  geom_rect(aes(fill = `Trophic State`, ymax = ymax, ymin = ymin, xmin = 3, xmax = 4)) +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) +
  ylab("Percent of Lakes") +
  facet_wrap(~name)

# # waffle
# library(waffle)
# 
# total_cells <- 41.5
# dt_waffle <- dt %>% 
#   dplyr::rename(trophic_state = `Trophic State`) %>%
#   tidyr::gather(key = "key", value = "value", -trophic_state) %>%
#   dplyr::filter(key == "This Study") %>%
#   mutate(value = floor((value / 100) * total_cells)) %>%
#   arrange(trophic_state)
# # sum(dt_waffle$value)
# # add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
# 
# ggplot(dt_waffle,
#        aes(fill = trophic_state, values = value)) +
#   geom_waffle(color = "white", size = 3, n_rows = 4, flip = FALSE) +
#   # facet_wrap(~key, ncol = 1) +
#   scale_x_discrete(expand = c(0,0)) +
#   scale_y_discrete(expand = c(0,0)) +
#   shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
#                     shades::delta(-10)) +
#   coord_equal() +
#   theme_enhance_waffle() + 
#   theme(strip.background = element_blank(), 
#         rect = element_rect(fill = "transparent"), 
#         legend.position = "bottom", 
#         title = element_blank(), 
#         strip.text = element_text(size = 16), 
#         legend.text = element_text(size = 10), 
#         legend.key.size = unit(0.5, "line")) + 
#   guides(fill = guide_legend(nrow = 1))
# 
# # highlighted regions
# test <- readRDS("../data/dt.rds") %>%
#   mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>%
#   dplyr::filter(!is.na(chla)) %>%
#   mutate(trophic_state = cut(chla, 
#                              breaks = c(-Inf, 2.6, 20, 56, Inf), 
#                              labels = c("oligotrophic", "mesotrophic", 
#                                         "eutrophic", "hypereutrophic"))) %>%
#   dplyr::select(lagoslakeid, is_focal, chla, hu4_zoneid, trophic_state) %>%
#   group_by(is_focal, trophic_state) %>%
#   count() %>%
#   tidyr::spread(trophic_state, n)
```

@@

## Model results when lake are restricted to > 40% watershed agriculture

```{r re-comparison_40-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN from six candidate models for lakes with greater than 40% watershed agricultural land-use. Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines). Also shown is a comparison to a zero effect (dashed line).", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-comparison_40-1.pdf")
```

@@

## Model results when land-use predictors are excluded
